### 2021-08-22 plos_latex_template.tex
RJ: edited accessibility rule

Next, think about set measurable indicators of success when organizing a diverse conference. The numbers resulting from these indicators are not the primary goal. Instead, this vision should guide and help hold the organizing team accountable towards these diverse and inclusive goals.

@@

\section{Rule X: Have an inclusive and diverse organizing team}
A genuinely inclusive conference can only be organized by an inclusive and diverse organizing team. Build a team with people from different regions, genders, socioeconomic statuses, and other aspects of diversity. Particular attention should be paid to the usually underrepresented groups (see \textbf{Rule 1} discussing the dimensions of diversity lacking in your community and event). To ensure a deeper understanding of the challenges in different diverse groups, it is essential to create a representative working group that functions as a snapshot of the community at large. But this will only work if there is real inclusion. One would be surprised by how often conference leads tend to do everything themselves instead of reaching out to the right people for the right task -- likely because the latter involves careful planning and communication well ahead of time or because they naively overestimate their expertise in areas they lack practical experience in. For example, a cisgender or abled person estimating what might work best for transgender people or people with sensory disabilities. The same holds for other dimensions of diversity. A truly inclusive and welcoming space is one in which everyone in the team is invited and allowed to bring their experience to bear. Even if creating and maintaining such a team and space is challenging, the positive outcomes far outweigh any minor inconveniences (e.g. time zones), and the team will grow, learn, and embrace more inclusive practices \cite{hong_groups_2004}.

@@

Conferences are often inaccessible to people with hearing, visual, and other disabilities \cite{price_access_2009}. People may also find conferences inaccessible due to their caring responsibilities, dietary restrictions, religious practices, or LGBTQ+ status. Each of these groups should be considered at every stage of the planning process. Welcoming people from these groups into the organizing team would allow them to take part in the decisions from the beginning and spot right away the inaccessible practices that need to improve (see \textbf{Rule 2}). If the conference is in person, the venue must be accessible for people with mobility limitations. Accommodations such as a quiet space for neurodivergent people and a space for breastfeeding should also be provided. Images used in communications about the conference should be accompanied by alternative text, while videos should have both captions and sound. Platforms for conference registration and abstract submission, websites and chat platforms should be screen-reader friendly and keyboard accessible, with low technology requirements (hardware, software, and internet connection). These aspects should be tested well in advance of going live. Captioning for presentations should be available in more than one language if possible. If the conference is in-person, presenters should always speak into a microphone to make it easier for the hard of hearing and for captioners or interpreters to listen to them. Accessibility guidelines for slides and presentations should be provided to the presenters, and their use should be encouraged (see \url{https://user2021.r-project.org/participation/accessibility/} for example). Among other things, the speakers should provide raw and accessible material to their talks before the conference, e.g., R Markdown, HTML, or \TeX{} files; if they prerecord their presentation, they should include their video and ensure that their face is visible so that deaf and hard-of-hearing people can read their lips if needed. Adding captions to recorded videos is relatively easy these days and is helpful to deaf and hard-of-hearing people, non-native speakers, and everyone in general.  Accessibility awards at the end of the conference are an excellent way to acknowledge the speakers who were mindful of inclusiveness when preparing and delivering their talks.

Accessibility practices are not afterthoughts that can be dealt with at the last minute. They require time and early decision-making \cite{irish_increasing_2020}. Conversely, inaccessible decisions are hard to course-correct, e.g., when finding out too late that a venue is inaccessible for wheelchairs in an in-person conference. 
Bear in mind that most accessibility practices are beneficial to everyone. Captions, for instance, are used by non-native speakers and people that access the conference in loud environments. The prior availability of material benefits people with low bandwidth and non-native speakers as well.

>>>>

Next, set measurable indicators of success when organizing a diverse conference. The numbers resulting from these indicators are not the primary goal. Instead, this vision should guide and help hold the organizing team accountable towards these diverse and inclusive goals.

@@

\section{Rule X: Have an inclusive and diverse organizing team}
\label{organizing_team}
A genuinely inclusive conference can only be organized by an inclusive and diverse organizing team. Build a team with people from different regions, genders, socioeconomic statuses, and other aspects of diversity. Particular attention should be paid to the usually underrepresented groups (see \textbf{Rule 1} discussing the dimensions of diversity lacking in your community and event). To ensure a deeper understanding of the challenges in different diverse groups, it is essential to create a representative working group that functions as a snapshot of the community at large. But this will only work if there is real inclusion. One would be surprised by how often conference leads tend to do everything themselves instead of reaching out to the right people for the right task -- likely because the latter involves careful planning and communication well ahead of time or because they naively overestimate their expertise in areas they lack practical experience in. For example, a cisgender or abled person estimating what might work best for transgender people or people with sensory disabilities. The same holds for other dimensions of diversity. A truly inclusive and welcoming space is one in which everyone in the team is invited and allowed to bring their experience to bear. Even if creating and maintaining such a team and space is challenging, the positive outcomes far outweigh any minor inconveniences (e.g. time zones), and the team will grow, learn, and embrace more inclusive practices \cite{hong_groups_2004}.

@@

Conferences are often inaccessible to people with hearing, visual, and other disabilities \cite{price_access_2009}. People may also find conferences inaccessible due to their caring responsibilities, dietary restrictions, religious practices, or LGBTQ+ status.
Inaccessible practices only exclude people from conferences, while accessible practices are inclusive and can be beneficial to a broad spectrum of people. For instance, having captions is helpful to deaf and hard-of-hearing people, non-native speakers, and everyone in general.

If the conference is in person, the venue must be accessible for people with mobility limitations. 
Accommodations such as a quiet space for neurodivergent people and a space for breastfeeding should also be provided.
Presenters should always speak into a microphone to make it easier for the hard of hearing and for captioners or interpreters to listen to them. 
Regardless of the conference format --online, in person or hybrid --images used in communications about the conference should be accompanied by alternative text, while videos should have both captions and sound. 
Platforms for conference registration and abstract submission, websites and chat platforms --if used --should be screen-reader friendly and keyboard accessible, with low technology requirements (hardware, software, and internet connection). 
Captioning for presentations should be available in more than one language if possible.
These aspects should be tested well in advance of going live.

Some practices, such as making accessible slides and presentations, will require great efforts from the presenters if they are not used to them. 
For that reason, the organizing team should provide accessibility guidelines for slides and presentations, encourage their use, and be available for any questions they may have.  
Among other things, the guidelines should ask for raw and accessible material to the talks before the conference, e.g., R Markdown, HTML, or \TeX{} files; if presentations are pre-recorded, the speakers should include their video and ensure that their face is visible so that deaf and hard-of-hearing people can read their lips if needed (see \url{https://user2021.r-project.org/participation/accessibility/} for example). 
Accessibility awards at the end of the conference are an excellent way to acknowledge the speakers who were mindful of inclusiveness when preparing and delivering their talks.

Most importantly, accessibility practices are not afterthoughts that can be dealt with at the last minute. 
They require time and early decision-making \cite{irish_increasing_2020}. 
Conversely, inaccessible decisions are hard to course-correct, e.g., when finding out too late that a venue is inaccessible for wheelchairs in an in-person conference. 
Welcoming people that are usually disabled by standard practices in conferences into the organizing team would allow them to take part in the decisions from the beginning and spot right away the inaccessible practices that need to improve (see \textbf{Rule \ref{organizing_team}}).
